### 2010-12-07 trunk/htdocs/user.tex
Added the liquid crystal activity constant zeta
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1159 40876441-3496-0410-a613-a2fca35b2ae2
Updated intructions to replace CVS by SVN
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1181 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  user.tex
%
%  The 'user' section which holds an overview, and discusses
%  compilation and running.
%
%  $Id: user.tex,v 1.1 2010-10-21 18:05:50 kevin Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2010 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We have a NeSCForge project account available at

\texttt{http://forge.nesc.ac.uk/projects/ludwig/}

This provides controlled access to known persons and provide CVS, bug
tracking, and so on. The NeSCForge CVS is not available to the public.

\textbf{IMPORTANT:} NeSCForge is scheduled to go out of service on 20th
December 2010. KS will announce an alternative as soon as possible.
This may mean some disruption.

To download, e.g., the \texttt{src} module, you need
\begin{verbatim}
cvs -z3 -d:ext:developername@forge.nesc.ac.uk:/cvsroot/ludwig co src
\end{verbatim}
where \texttt{developername} is replaced by your Nescforge user name.
(Note that this requires secure shell; you may need to set the
environment variable \texttt{CVS\_RSH=ssh} if you do not appear
to be getting any response.)

Currently, you need to download at least the cvs modules \texttt{src},
and \texttt{mpi\_s}. The \texttt{mpi\_s} module contains a `stub'
library to replace MPI in serial, and is required to run in serial.
This documentation is in the module
\texttt{htdocs}, unit tests are in \texttt{tests}, and the utilities
are in the module \texttt{util}.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  user.tex
%
%  The 'user' section which holds an overview, and discusses
%  compilation and running.
%
%  $Id: user.tex,v 1.2 2010-11-02 17:38:48 jlintuvu Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2010 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Under the auspices of the CCPs (Collaborative Computational Projects),
and in particular CCP5, we have a CCPForge project account at

\texttt{http://ccpforge.cse.rl.ac.uk/}

This provides controlled access to known persons and uses version
control via SVN, and includes bug
tracking, and so on. The CCPForge SVN is not available to the public
at the present time. You need to create an account at CCPForge, and
let me or Juho know the username so you can be added to the access list.

To download the entire code, you need
\begin{verbatim}
svn checkout --username <user> http://ccpforge.cse.rl.ac.uk/svn/ludwig
\end{verbatim}
where \texttt{<user>} is replaced by your CCPForge user name.
Note that this will download all the existing tags and branches
into a new directory named \texttt{ludwig}, as well as the main code!
On success, you should see three directories
\begin{verbatim}
$ ls ludwig
branches  tags      trunk
\end{verbatim}
The main code is in the \texttt{trunk} subdirectory. This documentation is
found in the file \texttt{trunk/htdocs/ludwig.tex}, unit tests are in
the directory \texttt{trunk/tests}, and the utilities are in
\texttt{trunk/util}, and so on.

If you do not want all the tags and branches (which take up a certain amount
of space), you can specify that you
want only the trunk, e.g.,
\begin{verbatim}
svn co --username <user> http://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk
\end{verbatim}
in which case you will get a new directory called \texttt{trunk} containing
the source files. All the instructions below refer to paths relative to
this trunk directory.

If you have problems, it may be worth while looking at the issue
tracker on the project web page. It would be useful if all issues
could be reported via this mechanism. If you e-mail me, I will just
insert your e-mail into the issue tracker!

@@

\inputkey{lc\_active\_zeta} Apolar liquid crystal activity constant.
